\begin{longtable}{@{\hskip0pt} p{10cm} | p{6cm} @{\hskip0pt}}
2.\enspace Et secúndum multitúdinem miseratiónum tu\textbf{á}rum,~* dele iniqui\textit{tá}\textit{tem} \textbf{me}am.
 & \textit{\small And according to the multitude of thy tender mercies blot out my iniquity.
}\\
3.\enspace Amplius lava me ab iniquitáte \textbf{me}a:~* et a peccáto \textit{me}\textit{o} \textbf{mun}da me.
 & \textit{\small Wash me yet more from my iniquity, and cleanse me from my sin.
}\\
4.\enspace Quóniam iniquitátem meam ego co\textbf{gnós}co:~* et peccátum meum contra \textit{me} \textit{est} \textbf{sem}per.
 & \textit{\small For I know my iniquity, and my sin is always before me.
}\\
5.\enspace Tibi soli peccávi, et malum coram te \textbf{fe}ci:~* ut justificéris in sermónibus tuis, et vincas cum \textit{ju}\textit{di}\textbf{cá}ris.
 & \textit{\small To thee only have I sinned, and have done evil before thee: that thou mayst be justified in thy words, and mayst overcome when thou art judged.
}\\
6.\enspace Ecce enim in iniquitátibus con\textbf{cép}tus sum:~* et in peccátis concépit me \textit{ma}\textit{ter} \textbf{me}a.
 & \textit{\small For behold I was conceived in iniquities; and in sins did my mother conceive me.
}\\
7.\enspace Ecce enim veritátem dile\textbf{xís}ti:~* incérta et occúlta sapiéntiæ tuæ manifes\textit{tás}\textit{ti} \textbf{mi}hi.
 & \textit{\small For behold thou hast loved truth: the uncertain and hidden things of thy wisdom thou hast made manifest to me.
}\\
8.\enspace Aspérges me hyssópo, et mun\textbf{dá}bor:~* lavábis me, et super nivem \textit{de}\textit{al}\textbf{bá}bor.
 & \textit{\small Thou shalt sprinkle me with hyssop, and I shall be cleansed: thou shalt wash me, and I shall be made whiter than snow.
}\\
9.\enspace Audítui meo dabis gáudium et læ\textbf{tí}tiam:~* et exsultábunt ossa hu\textit{mi}\textit{li}\textbf{á}ta.
 & \textit{\small To my hearing thou shalt give joy and gladness: and the bones that have been humbled shall rejoice.
}\\
10.\enspace Avérte fáciem tuam a peccátis \textbf{me}is:~* et omnes iniquitátes \textit{me}\textit{as} \textbf{de}le.
 & \textit{\small Turn away thy face from my sins, and blot out all my iniquities.
}\\
11.\enspace Cor mundum crea in me, \textbf{De}us:~* et spíritum rectum ínnova in viscé\textit{ri}\textit{bus} \textbf{me}is.
 & \textit{\small Create a clean heart in me, O God: and renew a right spirit within my bowels.
}\\
12.\enspace Ne projícias me a fácie \textbf{tu}a:~* et spíritum sanctum tuum ne áu\textit{fe}\textit{ras} \textbf{a} me.
 & \textit{\small Cast me not away from thy face; and take not thy holy spirit from me.
}\\
13.\enspace Redde mihi lætítiam salutáris \textbf{tu}i:~* et spíritu principá\textit{li} \textit{con}\textbf{fír}ma me.
 & \textit{\small Restore unto me the joy of thy salvation, and strengthen me with a perfect spirit.
}\\
14.\enspace Docébo iníquos vias \textbf{tu}as:~* et ímpii ad te \textit{con}\textit{ver}\textbf{tén}tur.
 & \textit{\small I will teach the unjust thy ways: and the wicked shall be converted to thee.
}\\
15.\enspace Líbera me de sanguínibus, Deus, Deus salútis \textbf{me}æ:~* et exsultábit lingua mea justí\textit{ti}\textit{am} \textbf{tu}am.
 & \textit{\small Deliver me from blood, O God, thou God of my salvation: and my tongue shall extol thy justice.
}\\
16.\enspace Dómine, lábia mea a\textbf{pé}ries:~* et os meum annuntiábit \textit{lau}\textit{dem} \textbf{tu}am.
 & \textit{\small O Lord, thou wilt open my lips: and my mouth shall declare thy praise.
}\\
17.\enspace Quóniam si voluísses sacrifícium, dedíssem \textbf{ú}tique:~* holocáustis non \textit{de}\textit{lec}\textbf{tá}beris.
 & \textit{\small For if thou hadst desired sacrifice, I would indeed have given it: with burnt offerings thou wilt not be delighted.
}\\
18.\enspace Sacrifícium Deo spíritus contribu\textbf{lá}tus:~* cor contrítum et humiliátum, Deus, \textit{non} \textit{de}\textbf{spí}cies.
 & \textit{\small A sacrifice to God is an afflicted spirit: a contrite and humbled heart, O God, thou wilt not despise.
}\\
19.\enspace Benígne fac, Dómine, in bona voluntáte tua \textbf{Si}on:~* ut ædificéntur mu\textit{ri} \textit{Je}\textbf{rú}salem.
 & \textit{\small Deal favourably, O Lord, in thy good will with Sion; that the walls of Jerusalem may be built up.
}\\
20.\enspace Tunc acceptábis sacrifícium justítiæ, oblatiónes, et holo\textbf{cáus}ta:~* tunc impónent super altáre \textit{tu}\textit{um} \textbf{ví}tulos. & \textit{\small Then shalt thou accept the sacrifice of justice, oblations and whole burnt offerings: then shall they lay calves upon thy altar.}\\
\end{longtable}