\begin{longtable}{@{\hskip0pt} p{9.5cm} | p{6.5cm} @{\hskip0pt}}
2.\enspace Infíxus sum in limo pro\textbf{fún}di:~* et non \textit{est} \textit{sub}\textbf{stán}tia.
 & \textit{\small I stick fast in the mire of the deep: * and there is no sure standing.
}\\
3.\enspace Veni in altitúdinem \textbf{ma}ris:~* et tempés\textit{tas} \textit{de}\textbf{mér}sit me.
 & \textit{\small I am come into the depth of the sea: * and a tempest hath overwhelmed me.
}\\
4.\enspace Laborávi clamans, raucæ factæ sunt fauces \textbf{me}æ:~* defecérunt óculi mei, dum spero in \textit{De}\textit{um} \textbf{me}um.
 & \textit{\small I have laboured with crying; my jaws are become hoarse: * my eyes have failed, whilst I hope in my God.
}\\
5.\enspace Multiplicáti sunt super capíllos cápitis \textbf{me}i,~* qui odé\textit{runt} \textit{me} \textbf{gra}tis.
 & \textit{\small They are multiplied above the hairs of my head, * who hate me without cause.
}\\
6.\enspace Confortáti sunt qui persecúti sunt me inimíci mei in\textbf{jús}te:~* quæ non rápui, tunc \textit{ex}\textit{sol}\textbf{vé}bam.
 & \textit{\small My enemies are grown strong who have wrongfully persecuted me: * then did I pay that which I took not away.
}\\
7.\enspace Deus, tu scis insipiéntiam \textbf{me}am:~* et delícta mea a te non \textit{sunt} \textit{abs}\textbf{cón}dita.
 & \textit{\small O God, thou knowest my foolishness; * and my offences are not hidden from thee.
}\\
8.\enspace Non erubéscant in me qui exspéctant te, \textbf{Dó}mine,~* Dómi\textit{ne} \textit{vir}\textbf{tú}tum
 & \textit{\small Let not them be ashamed for me, who look for thee, O Lord, * the Lord of hosts.
}\\
9.\enspace Non confundántur \textbf{su}per me~* qui quærunt te, \textit{De}\textit{us} \textbf{Is}raël.
 & \textit{\small Let them not be confounded on my account, * who seek thee, O God of Israel.
}\\
10.\enspace Quóniam propter te sustínui op\textbf{pró}brium:~* opéruit confúsio fá\textit{ci}\textit{em} \textbf{me}am.
 & \textit{\small Because for thy sake I have borne reproach; * shame hath covered my face.
}\\
11.\enspace Extráneus factus sum frátribus \textbf{me}is,~* et peregrínus fíliis \textit{ma}\textit{tris} \textbf{me}æ.
 & \textit{\small I am become a stranger to my brethren, * and an alien to the sons of my mother.
}\\
12.\enspace Quóniam zelus domus tuæ com\textbf{é}dit me:~* et oppróbria exprobrántium tibi ceci\textit{dé}\textit{runt} \textbf{su}per me.
 & \textit{\small For the zeal of thy house hath eaten me up: * and the reproaches of them that reproached thee are fallen upon me.
}\\
13.\enspace Et opérui in jejúnio ánimam \textbf{me}am:~* et factum est in oppró\textit{bri}\textit{um} \textbf{mi}hi.
 & \textit{\small And I covered my soul in fasting: * and it was made a reproach to me.
}\\
14.\enspace Et pósui vestiméntum meum ci\textbf{lí}cium:~* et factus sum illis \textit{in} \textit{pa}\textbf{rá}bolam.
 & \textit{\small And I made haircloth my garment: * and I became a byword to them.
}\\
15.\enspace Advérsum me loquebántur, qui sedébant in \textbf{por}ta:~* et in me psallébant qui bi\textit{bé}\textit{bant} \textbf{vi}num.
 & \textit{\small They that sat in the gate spoke against me: * and they that drank wine made me their song.
}\\
16.\enspace Ego vero oratiónem meam ad te, \textbf{Dó}mine:~* tempus beneplá\textit{ci}\textit{ti}, \textbf{De}us.
 & \textit{\small But as for me, my prayer is to thee, O Lord; * for the time of thy good pleasure, O God.
}\\
17.\enspace In multitúdine misericórdiæ tuæ ex\textbf{áu}di me,~* in veritáte sa\textit{lú}\textit{tis} \textbf{tu}æ:
 & \textit{\small In the multitude of thy mercy hear me, * in the truth of thy salvation.
}\\
18.\enspace Eripe me de luto, ut non in\textbf{fí}gar:~* líbera me ab iis, qui odérunt me, et de profún\textit{dis} \textit{a}\textbf{quá}rum.
 & \textit{\small Draw me out of the mire, that I may not stick fast: * deliver me from them that hate me, and out of the deep waters.
}\\
19.\enspace Non me demérgat tempéstas aquæ,~\GreDagger\ neque absórbeat me pro\textbf{fún}dum:~* neque úrgeat super me púte\textit{us} \textit{os} \textbf{su}um.
 & \textit{\small Let not the tempest of water drown me, nor the deep swallow me up: * and let not the pit shut her mouth upon me.
}\\
20.\enspace Exáudi me, Dómine, quóniam benígna est misericórdia \textbf{tu}a:~* secúndum multitúdinem miseratiónum tuárum ré\textit{spi}\textit{ce} \textbf{in} me.
 & \textit{\small Hear me, O Lord, for thy mercy is kind; * look upon me according to the multitude of thy tender mercies.
}\\
21.\enspace Et ne avértas fáciem tuam a púero \textbf{tu}o:~* quóniam tríbulor, velóci\textit{ter} \textit{ex}\textbf{áu}di me.
 & \textit{\small And turn not away thy face from thy servant: * for I am in trouble, hear me speedily.
}\\
22.\enspace Inténde ánimæ meæ, et líbera \textbf{e}am:~* propter inimícos meos \textit{é}\textit{ri}\textbf{pe} me.
 & \textit{\small Attend to my soul, and deliver it: * save me because of my enemies.
}\\
23.\enspace Tu scis impropérium meum, et confusiónem \textbf{me}am,~* et reverén\textit{ti}\textit{am} \textbf{me}am.
 & \textit{\small Thou knowest my reproach, and my confusion, * and my shame.
}\\
24.\enspace In conspéctu tuo sunt omnes qui tríbu\textbf{lant} me:~* impropérium exspectávit cor meum, \textit{et} \textit{mi}\textbf{sé}riam.
 & \textit{\small In thy sight are all they that afflict me; * my heart hath expected reproach and misery.
}\\
25.\enspace Et sustínui qui simul contristarétur, et non \textbf{fu}it:~* et qui consolarétur, et \textit{non} \textit{in}\textbf{vé}ni.
 & \textit{\small And I looked for one that would grieve together with me, * but there was none: and for one that would comfort me, and I found none.
}\\
26.\enspace Et dedérunt in escam \textbf{me}am fel:~* et in siti mea potavérunt \textit{me} \textit{a}\textbf{cé}to.
 & \textit{\small And they gave me gall for my food, * and in my thirst they gave me vinegar to drink.
}\\
27.\enspace Fiat mensa eórum coram ipsis in \textbf{lá}queum,~* et in retributiónes, \textit{et} \textit{in} \textbf{scán}dalum.
 & \textit{\small Let their table become as a snare before them, * and a recompense, and a stumblingblock.
}\\
28.\enspace Obscuréntur óculi eórum ne \textbf{ví}deant:~* et dorsum eórum sem\textit{per} \textit{in}\textbf{cúr}va.
 & \textit{\small Let their eyes be darkened that they see not; * and their back bend thou down always.
}\\
29.\enspace Effúnde super eos iram \textbf{tu}am:~* et furor iræ tuæ compre\textit{hén}\textit{dat} \textbf{e}os.
 & \textit{\small Pour out thy indignation upon them: * and let thy wrathful anger take hold of them.
}\\
30.\enspace Fiat habitátio eórum de\textbf{sér}ta:~* et in tabernáculis eórum non sit \textit{qui} \textit{in}\textbf{há}bitet.
 & \textit{\small Let their habitation be made desolate: * and let there be none to dwell in their tabernacles.
}\\
31.\enspace Quóniam quem tu percussísti, perse\textbf{cú}ti sunt:~* et super dolórem vúlnerum meórum \textit{ad}\textit{di}\textbf{dé}runt.
 & \textit{\small Because they have persecuted him whom thou hast smitten; * and they have added to the grief of my wounds.
}\\
32.\enspace Appóne iniquitátem super iniquitátem e\textbf{ó}rum:~* et non intrent in justí\textit{ti}\textit{am} \textbf{tu}am.
 & \textit{\small Add thou iniquity upon their iniquity: * and let them not come into thy justice.
}\\
33.\enspace Deleántur de libro vi\textbf{vén}tium:~* et cum justis \textit{non} \textit{scri}\textbf{bán}tur.
 & \textit{\small Let them be blotted out of the book of the living; * and with the just let them not be written.
}\\
34.\enspace Ego sum pauper et \textbf{do}lens:~* salus tua, De\textit{us}, \textit{su}\textbf{scé}pit me.
 & \textit{\small I am poor and sorrowful: * thy salvation, O God, hath set me up.
}\\
35.\enspace Laudábo nomen Dei cum \textbf{cán}tico:~* et magnificábo e\textit{um} \textit{in} \textbf{lau}de:
 & \textit{\small I will praise the name of God with a canticle: * and I will magnify him with praise.
}\\
36.\enspace Et placébit Deo super vítulum no\textbf{vél}lum:~* córnua producén\textit{tem} \textit{et} \textbf{ún}gulas.
 & \textit{\small And it shall please God better than a young calf, * that bringeth forth horns and hoofs.
}\\
37.\enspace Vídeant páuperes et læ\textbf{tén}tur:~* qu\'{\ae}rite Deum, et vivet á\textit{ni}\textit{ma} \textbf{ves}tra.
 & \textit{\small Let the poor see and rejoice: * seek ye God, and your soul shall live.
}\\
38.\enspace Quóniam exaudívit páuperes \textbf{Dó}minus:~* et vinctos suos \textit{non} \textit{de}\textbf{spé}xit.
 & \textit{\small For the Lord hath heard the poor: * and hath not despised his prisoners.
}\\
39.\enspace Laudent illum cæli et \textbf{ter}ra,~* mare et ómnia reptíli\textit{a} \textit{in} \textbf{e}is.
 & \textit{\small Let the heavens and the earth praise him; * the sea, and every thing that creepeth therein.
}\\
40.\enspace Quóniam Deus salvam fáciet \textbf{Si}on:~* et ædificabúntur civi\textit{tá}\textit{tes} \textbf{Ju}da.
 & \textit{\small For God will save Sion, * and the cities of Juda shall be built up.
}\\
41.\enspace Et inhabitábunt \textbf{i}bi,~* et hereditáte ac\textit{quí}\textit{rent} \textbf{e}am.
 & \textit{\small And they shall dwell there, * and acquire it by inheritance.
}\\
42.\enspace Et semen servórum ejus possidébit \textbf{e}am:~* et qui díligunt nomen ejus, habitá\textit{bunt} \textit{in} \textbf{e}a. & \textit{\small And the seed of his servants shall possess it; * and they that love his name shall dwell therein.}\\
\end{longtable}