\begin{longtable}{@{\hskip0pt} p{10cm} | p{6cm} @{\hskip0pt}}
2.\enspace Inclína ad me aurem \textbf{tu}am,~* \textit{et} \textbf{sal}va me.
 & \textit{\small Incline thy ear unto me, and save me.
}\\
3.\enspace Esto mihi in Deum protectórem, et in locum mu\textbf{ní}tum:~* ut sal\textit{vum} \textit{me} \textbf{fá}cias.
 & \textit{\small Be thou unto me a God, a protector, and a place of strength: that thou mayst make me safe.
}\\
4.\enspace Quóniam firmaméntum \textbf{me}um,~* et refúgium \textit{me}\textit{um} \textbf{es} tu.
 & \textit{\small For thou art my firmament and my refuge.
}\\
5.\enspace Deus meus, éripe me de manu pecca\textbf{tó}ris,~* et de manu contra legem agéntis \textit{et} \textit{in}\textbf{í}qui:
 & \textit{\small Deliver me, O my God, out of the hand of the sinner, and out of the hand of the transgressor of the law and of the unjust.
}\\
6.\enspace Quóniam tu es patiéntia mea, \textbf{Dó}mine:~* Dómine, spes mea a juven\textit{tú}\textit{te} \textbf{me}a.
 & \textit{\small For thou art my patience, O Lord: my hope, O Lord, from my youth.
}\\
7.\enspace In te confirmátus sum ex \textbf{ú}tero:~* de ventre matris meæ tu es pro\textit{téc}\textit{tor} \textbf{me}us.
 & \textit{\small By thee have I been confirmed from the womb: from my mother’s womb thou art my protector.
}\\
8.\enspace In te cantátio mea semper:~\GreDagger\ tamquam prodígium factus sum \textbf{mul}tis:~* et tu ad\textit{jú}\textit{tor} \textbf{for}tis.
 & \textit{\small Of thee shall I continually sing: I am become unto many as a wonder, but thou art a strong helper.
}\\
9.\enspace Repleátur os meum laude, ut cantem glóriam \textbf{tu}am:~* tota die magnitú\textit{di}\textit{nem} \textbf{tu}am.
 & \textit{\small Let my mouth be filled with praise, that I may sing thy glory; thy greatness all the day long.
}\\
10.\enspace Ne projícias me in témpore senec\textbf{tú}tis:~* cum defécerit virtus mea, ne \textit{de}\textit{re}\textbf{lín}quas me.
 & \textit{\small Cast me not off in the time of old age: when my strength shall fail, do not thou forsake me.
}\\
11.\enspace Quia dixérunt inimíci mei \textbf{mi}hi:~* et qui custodiébant ánimam meam, consílium fecé\textit{runt} \textit{in} \textbf{u}num.
 & \textit{\small For my enemies have spoken against me; and they that watched my soul have consulted together,
}\\
12.\enspace Dicéntes: Deus derelíquit eum,~\GreDagger\ persequímini, et comprehéndite \textbf{e}um:~* quia non est \textit{qui} \textit{e}\textbf{rí}piat.
 & \textit{\small Saying: God hath forsaken him: pursue and take him, for there is none to deliver him.
}\\
13.\enspace Deus ne elongéris \textbf{a} me:~* Deus meus, in auxílium \textit{me}\textit{um} \textbf{ré}spice.
 & \textit{\small O God, be not thou far from me: O my God, make haste to my help.
}\\
14.\enspace Confundántur, et defíciant detrahéntes ánimæ \textbf{me}æ:~* operiántur confusióne et pudóre, qui quærunt \textit{ma}\textit{la} \textbf{mi}hi.
 & \textit{\small Let them be confounded and come to nothing that detract my soul; let them be covered with confusion and shame that seek my hurt.
}\\
15.\enspace Ego autem semper spe\textbf{rá}bo:~* et adjíciam super omnem \textit{lau}\textit{dem} \textbf{tu}am.
 & \textit{\small But I will always hope; and will add to all thy praise.
}\\
16.\enspace Os meum annuntiábit justítiam \textbf{tu}am:~* tota die salu\textit{tá}\textit{re} \textbf{tu}um.
 & \textit{\small My mouth shall shew forth thy justice; thy salvation all the day long.
}\\
17.\enspace Quóniam non cognóvi litteratúram,~\GreDagger\ introíbo in poténtias \textbf{Dó}mini:~* Dómine, memorábor justítiæ tu\textit{æ} \textit{so}\textbf{lí}us.
 & \textit{\small Because I have not known learning, I will enter into the powers of the Lord: O Lord, I will be mindful of thy justice alone.
}\\
18.\enspace Deus, docuísti me a juventúte \textbf{me}a:~* et usque nunc pronuntiábo mirabí\textit{li}\textit{a} \textbf{tu}a.
 & \textit{\small Thou hast taught me, O God, from my youth: and till now I will declare thy wonderful works.
}\\
19.\enspace Et usque in senéctam et \textbf{sé}nium:~* Deus, ne \textit{de}\textit{re}\textbf{lín}quas me,
 & \textit{\small And unto old age and grey hairs: O God, forsake me not,
}\\
20.\enspace Donec annúntiem bráchium \textbf{tu}um~* generatióni omni, \textit{quæ} \textit{ven}\textbf{tú}ra est:
 & \textit{\small Until I shew forth thy arm to all the generation that is to come:
}\\
21.\enspace Poténtiam tuam, et justítiam tuam, Deus,~\GreDagger\ usque in altíssima, quæ fecísti ma\textbf{gná}lia:~* Deus, quis sí\textit{mi}\textit{lis} \textbf{ti}bi?
 & \textit{\small Thy power, and thy justice, O God, even to the highest great things thou hast done: O God, who is like to thee?
}\\
22.\enspace Quantas ostendísti mihi tribulatiónes multas et malas:~\GreDagger\ et convérsus vivifi\textbf{cás}ti me:~* et de abýssis terræ íterum \textit{re}\textit{du}\textbf{xís}ti me:
 & \textit{\small How great troubles hast thou shewn me, many and grievous: and turning thou hast brought me to life, and hast brought me back again from the depths of the earth:
}\\
23.\enspace Multiplicásti magnificéntiam \textbf{tu}am:~* et convérsus conso\textit{lá}\textit{tus} \textbf{es} me.
 & \textit{\small Thou hast multiplied thy magnificence; and turning to me thou hast comforted me.
}\\
24.\enspace Nam et ego confitébor tibi in vasis psalmi veritátem \textbf{tu}am:~* Deus, psallam tibi in cíthara, \textit{Sanc}\textit{tus} \textbf{Is}raël.
 & \textit{\small For I will also confess to thee thy truth with the instruments of psaltery: O God, I will sing to thee with the harp,
}\\
25.\enspace Exsultábunt lábia mea cum cantávero \textbf{ti}bi:~* et ánima mea, quam \textit{red}\textit{e}\textbf{mís}ti.
 & \textit{\small My lips shall greatly rejoice, when I shall sing to thee; and my soul which thou hast redeemed.
}\\
26.\enspace Sed et lingua mea tota die meditábitur justítiam \textbf{tu}am:~* cum confúsi et revériti fúerint, qui quærunt \textit{ma}\textit{la} \textbf{mi}hi. & \textit{\small Yea and my tongue shall meditate on thy justice all the day; when they shall be confounded and put to shame that seek evils to me.}\\
\end{longtable}