\begin{longtable}{@{\hskip0pt} p{10cm} | p{6cm} @{\hskip0pt}}
2.\enspace Judicáre pópulum tuum \textbf{in} jus\textbf{tí}tia,~* et páuperes tuos \textbf{in} ju\textbf{dí}cio.
 & \textit{\small To judge thy people with justice, and thy poor with judgment.
}\\
3.\enspace Suscípiant montes \textbf{pa}cem \textbf{pó}pulo:~* et \textbf{col}les jus\textbf{tí}tiam.
 & \textit{\small Let the mountains receive peace for the people: and the hills justice.
}\\
4.\enspace Judicábit páuperes pópuli, et salvos fáciet \textbf{fí}lios \textbf{páu}perum:~* et humiliábit calum\textbf{ni}a\textbf{tó}rem.
 & \textit{\small He shall judge the poor of the people, and he shall save the children of the poor: and he shall humble the oppressor.
}\\
5.\enspace Et permanébit cum sole, et \textbf{an}te \textbf{lu}nam,~* in generatióne et gene\textbf{ra}ti\textbf{ó}nem.
 & \textit{\small And he shall continue with the sun, and before the moon, throughout all generations.
}\\
6.\enspace Descéndet sicut plúvi\textbf{a} in \textbf{vel}lus:~* et sicut stillicídia stillántia \textbf{su}per \textbf{ter}ram.
 & \textit{\small He shall come down like rain upon the fleece; and as showers falling gently upon the earth.
}\\
7.\enspace Oriétur in diébus ejus justítia, et abun\textbf{dán}tia \textbf{pa}cis:~* donec aufe\textbf{rá}tur \textbf{lu}na.
 & \textit{\small In his days shall justice spring up, and abundance of peace, till the moon be taken away.
}\\
8.\enspace Et dominábitur a mari \textbf{us}que ad \textbf{ma}re:~* et a flúmine usque ad términos \textbf{or}bis ter\textbf{rá}rum.
 & \textit{\small And he shall rule from sea to sea, and from the river unto the ends of the earth.
}\\
9.\enspace Coram illo próci\textbf{dent} Æ\textbf{thí}opes:~* et inimíci ejus \textbf{ter}ram \textbf{lin}gent.
 & \textit{\small Before him the Ethiopians shall fall down: and his enemies shall lick the ground.
}\\
10.\enspace Reges Tharsis, et ínsulæ \textbf{mú}nera \textbf{óf}ferent:~* reges Arabum et Saba \textbf{do}na ad\textbf{dú}cent.
 & \textit{\small The kings of Tharsis and the islands shall offer presents: the kings of the Arabians and of Saba shall bring gifts:
}\\
11.\enspace Et adorábunt eum omnes \textbf{re}ges \textbf{ter}ræ:~* omnes Gentes \textbf{sér}vient \textbf{e}i:
 & \textit{\small And all kings of the earth shall adore him: all nations shall serve him.
}\\
12.\enspace Quia liberábit páuperem \textbf{a} pot\textbf{én}te:~* et páuperem, cui non \textbf{e}rat ad\textbf{jú}tor.
 & \textit{\small For he shall deliver the poor from the mighty: and the needy that had no helper.
}\\
13.\enspace Parcet páupe\textbf{ri} et \textbf{ín}opi:~* et ánimas páuperum \textbf{sal}vas \textbf{fá}ciet.
 & \textit{\small He shall spare the poor and needy: and he shall save the souls of the poor.
}\\
14.\enspace Ex usúris et iniquitáte rédimet áni\textbf{mas} e\textbf{ó}rum:~* et honorábile nomen eórum \textbf{co}ram \textbf{il}lo.
 & \textit{\small He shall redeem their souls from usuries and iniquity: and their names shall be honourable in his sight.
}\\
15.\enspace Et vivet, et dábitur ei de auro Arábiæ,~\GreDagger\ et adorábunt de \textbf{ip}so \textbf{sem}per:~* tota die bene\textbf{dí}cent \textbf{e}i.
 & \textit{\small And he shall live, and to him shall be given of the gold of Arabia, for him they shall always adore: they shall bless him all the day.
}\\
16.\enspace Et erit firmaméntum in terra in summis móntium,~\GreDagger\ superextollétur super Líbanum \textbf{fruc}tus \textbf{e}jus:~* et florébunt de civitáte sicut \textbf{fe}num \textbf{ter}ræ.
 & \textit{\small And there shall be a firmament on the earth on the tops of mountains, above Libanus shall the fruit thereof be exalted: and they of the city shall flourish like the grass of the earth.
}\\
17.\enspace Sit nomen ejus bene\textbf{díc}tum in \textbf{s\'{\ae}}cula:~* ante solem pérmanet \textbf{no}men \textbf{e}jus.
 & \textit{\small Let his name be blessed for evermore: his name continueth before the sun.
}\\
18.\enspace Et benedicéntur in ipso omnes \textbf{tri}bus \textbf{ter}ræ:~* omnes Gentes magnifi\textbf{cá}bunt \textbf{e}um.
 & \textit{\small And in him shall all the tribes of the earth be blessed: all nations shall magnify him.
}\\
19.\enspace Benedíctus Dóminus, \textbf{De}us \textbf{Is}raël,~* qui facit mira\textbf{bí}lia \textbf{so}lus.
 & \textit{\small Blessed be the Lord, the God of Israel, who alone doth wonderful things.
}\\
20.\enspace Et benedíctum nomen majestátis ejus \textbf{in} æ\textbf{tér}num:~* et replébitur majestáte ejus omnis terra: \textbf{fi}at, \textbf{fi}at. & \textit{\small And blessed be the name of his majesty for ever: and the whole earth shall be filled with his majesty. So be it. So be it.}\\
\end{longtable}