\begin{longtable}{@{\hskip0pt} p{10cm} | p{6cm} @{\hskip0pt}}
2.\enspace Mei autem pene moti sunt \textbf{pe}des:~* pene effúsi sunt \textit{gres}\textit{sus} \textbf{me}i.
 & \textit{\small But my feet were almost moved; my steps had wellnigh slipped.
}\\
3.\enspace Quia zelávi super in\textbf{í}quos,~* pacem pecca\textit{tó}\textit{rum} \textbf{vi}dens.
 & \textit{\small Because I had a zeal on occasion of the wicked, seeing the prosperity of sinners.
}\\
4.\enspace Quia non est respéctus morti e\textbf{ó}rum:~* et firmaméntum in pla\textit{ga} \textit{e}\textbf{ó}rum.
 & \textit{\small For there is no regard to their death, nor is there strength in their stripes.
}\\
5.\enspace In labóre hóminum \textbf{non} sunt:~* et cum homínibus non fla\textit{gel}\textit{la}\textbf{bún}tur:
 & \textit{\small They are not in the labour of men: neither shall they be scourged like other men.
}\\
6.\enspace Ideo ténuit eos su\textbf{pér}bia,~* opérti sunt iniquitáte et impie\textit{tá}\textit{te} \textbf{su}a.
 & \textit{\small Therefore pride hath held them fast: they are covered with their iniquity and their wickedness.
}\\
7.\enspace Pródiit quasi ex ádipe iníquitas e\textbf{ó}rum:~* transiérunt in af\textit{féc}\textit{tum} \textbf{cor}dis.
 & \textit{\small Their iniquity hath come forth, as it were from fatness: they have passed into the affection of the heart.
}\\
8.\enspace Cogitavérunt, et locúti sunt ne\textbf{quí}tiam:~* iniquitátem in excél\textit{so} \textit{lo}\textbf{cú}ti sunt.
 & \textit{\small They have thought and spoken wickedness: they have spoken iniquity on high.
}\\
9.\enspace Posuérunt in cælum os \textbf{su}um:~* et lingua eórum transí\textit{vit} \textit{in} \textbf{ter}ra.
 & \textit{\small They have set their mouth against heaven: and their tongue hath passed through the earth.
}\\
10.\enspace Ideo convertétur pópulus \textbf{me}us hic:~* et dies pleni invenién\textit{tur} \textit{in} \textbf{e}is.
 & \textit{\small Therefore will my people return here and full days shall be found in them.
}\\
11.\enspace Et dixérunt: Quómodo scit \textbf{De}us,~* et si est sciéntia \textit{in} \textit{ex}\textbf{cél}so?
 & \textit{\small And they said: How doth God know? and is there knowledge in the most High?
}\\
12.\enspace Ecce ipsi peccatóres, et abundántes in \textbf{s\'{\ae}}culo,~* obtinué\textit{runt} \textit{di}\textbf{ví}tias.
 & \textit{\small Behold these are sinners; and yet abounding in the world they have obtained riches.
}\\
13.\enspace Et dixi: Ergo sine causa justificávi cor \textbf{me}um,~* et lavi inter innocéntes \textit{ma}\textit{nus} \textbf{me}as.
 & \textit{\small And I said: Then have I in vain justified my heart, and washed my hands among the innocent.
}\\
14.\enspace Et fui flagellátus tota \textbf{di}e,~* et castigátio mea in \textit{ma}\textit{tu}\textbf{tí}nis.
 & \textit{\small And I have been scourged all the day; and my chastisement hath been in the mornings.
}\\
15.\enspace Si dicébam: Nar\textbf{rá}bo sic:~* ecce natiónem filiórum tuórum \textit{re}\textit{pro}\textbf{bá}vi.
 & \textit{\small If I said: I will speak thus; behold I should condemn the generation of thy children.
}\\
16.\enspace Existimábam ut cognósce\textbf{rem} hoc,~* la\textit{bor} \textit{est} \textbf{an}te me.
 & \textit{\small I studied that I might know this thing, it is a labour in my sight:
}\\
17.\enspace Donec intrem in Sanctuárium \textbf{De}i:~* et intélligam in novíssi\textit{mis} \textit{e}\textbf{ó}rum.
 & \textit{\small Until I go into the sanctuary of God, and understand concerning their last ends.
}\\
18.\enspace Verúmtamen propter dolos posuísti \textbf{e}is:~* dejecísti eos dum al\textit{le}\textit{va}\textbf{rén}tur.
 & \textit{\small But indeed for deceits thou hast put it to them: when they were lifted up, thou hast cast them down.
}\\
19.\enspace Quómodo facti sunt in desolatiónem, súbito defe\textbf{cé}runt:~* periérunt propter iniqui\textit{tá}\textit{tem} \textbf{su}am.
 & \textit{\small How are they brought to desolation? they have suddenly ceased to be: they have perished by reason of their iniquity.
}\\
20.\enspace Velut sómnium surgéntium, \textbf{Dó}mine,~* in civitáte tua imáginem ipsórum ad ní\textit{hi}\textit{lum} \textbf{réd}iges.
 & \textit{\small As the dream of them that awake, O Lord; so in thy city thou shalt bring their image to nothing.
}\\
21.\enspace Quia inflammátum est cor meum, et renes mei commu\textbf{tá}ti sunt:~* et ego ad níhilum redáctus sum, \textit{et} \textit{ne}\textbf{scí}vi.
 & \textit{\small For my heart hath been inflamed, and my reins have been changed: and I am brought to nothing, and I knew not.
}\\
22.\enspace Ut juméntum factus sum \textbf{a}pud te:~* et ego \textit{sem}\textit{per} \textbf{te}cum.
 & \textit{\small I am become as a beast before thee: and I am always with thee.
}\\
23.\enspace Tenuísti manum déxteram meam:~\GreDagger\ et in voluntáte tua dedu\textbf{xís}ti me,~* et cum glória \textit{su}\textit{sce}\textbf{pís}ti me.
 & \textit{\small Thou hast held me by my right hand; and by thy will thou hast conducted me, and with thy glory thou hast received me.
}\\
24.\enspace Quid enim mihi est in \textbf{cæ}lo?~* et a te quid vólui \textit{su}\textit{per} \textbf{ter}ram?
 & \textit{\small For what have I in heaven? and besides thee what do I desire upon earth?
}\\
25.\enspace Defécit caro mea, et cor \textbf{me}um:~* Deus cordis mei, et pars mea Deus \textit{in} \textit{æ}\textbf{tér}num.
 & \textit{\small For thee my flesh and my heart hath fainted away: thou art the God of my heart, and the God that is my portion for ever.
}\\
26.\enspace Quia ecce, qui elóngant se a te, per\textbf{í}bunt:~* perdidísti omnes, qui forni\textit{cán}\textit{tur} \textbf{abs} te.
 & \textit{\small For behold they that go far from thee shall perish: thou hast destroyed all them that are disloyal to thee.
}\\
27.\enspace Mihi autem adhærére Deo \textbf{bo}num est:~* pónere in Dómino De\textit{o} \textit{spem} \textbf{me}am:
 & \textit{\small But it is good for me to adhere to my God, to put my hope in the Lord God:
}\\
28.\enspace Ut annúntiem omnes prædicatiónes \textbf{tu}as,~* in portis fí\textit{li}\textit{æ} \textbf{Si}on. & \textit{\small That I may declare all thy praises, in the gates of the daughter of Sion.}\\
\end{longtable}