\begin{longtable}{@{\hskip0pt} p{10cm} | p{6cm} @{\hskip0pt}}
2.\enspace Memor esto congregati\textbf{ó}nis \textbf{tu}æ:~* quam possedísti \textit{ab} \textit{in}\textbf{í}tio.
 & \textit{\small Remember thy congregation, which thou hast possessed from the beginning.
}\\
3.\enspace Redemísti virgam heredi\textbf{tá}tis \textbf{tu}æ:~* mons Sion, in quo habitás\textit{ti} \textit{in} \textbf{e}o.
 & \textit{\small The sceptre of thy inheritance which thou hast redeemed: mount Sion in which thou hast dwelt.
}\\
4.\enspace Leva manus tuas in supérbias e\textbf{ó}rum in \textbf{fi}nem:~* quanta malignátus est inimí\textit{cus} \textit{in} \textbf{sanc}to!
 & \textit{\small Lift up thy hands against their pride unto the end; see what things the enemy hath done wickedly in the sanctuary.
}\\
5.\enspace Et gloriáti sunt \textbf{qui} o\textbf{dé}runt te:~* in médio solemni\textit{tá}\textit{tis} \textbf{tu}æ.
 & \textit{\small And they that hate thee have made their boasts, in the midst of thy solemnity.
}\\
6.\enspace Posuérunt signa \textbf{su}a, \textbf{si}gna:~* et non cognovérunt sicut in éxitu \textit{su}\textit{per} \textbf{sum}mum.
 & \textit{\small They have set up their ensigns for signs, and they knew not both in the going out and on the highest top.
}\\
7.\enspace Quasi in silva lignórum secúribus excidérunt jánuas ejus \textbf{in} id\textbf{íp}sum:~* in secúri et áscia deje\textit{cé}\textit{runt} \textbf{e}am.
 & \textit{\small As with axes in a wood of trees, they have cut down at once the gates thereof, with axe and hatchet they have brought it down.
}\\
8.\enspace Incendérunt igni sanctu\textbf{á}rium \textbf{tu}um:~* in terra polluérunt tabernáculum nó\textit{mi}\textit{nis} \textbf{tu}i.
 & \textit{\small They have set fire to thy sanctuary: they have defiled the dwelling place of thy name on the earth.
}\\
9.\enspace Dixérunt in corde suo cognátio e\textbf{ó}rum \textbf{si}mul:~* Quiéscere faciámus omnes dies festos De\textit{i} \textit{a} \textbf{ter}ra.
 & \textit{\small They said in their heart, the whole kindred of them together: Let us abolish all the festival days of God from the land.
}\\
10.\enspace Signa nostra non vídimus, jam non \textbf{est} pro\textbf{phé}ta:~* et nos non co\textit{gnó}\textit{scet} \textbf{ám}plius.
 & \textit{\small Our signs we have not seen, there is now no prophet: and he will know us no more.
}\\
11.\enspace Usquequo, Deus, improperábit \textbf{in}i\textbf{mí}cus:~* irrítat adversárius nomen tu\textit{um} \textit{in} \textbf{fi}nem?
 & \textit{\small How long, O God, shall the enemy reproach: is the adversary to provoke thy name for ever?
}\\
12.\enspace Ut quid avértis manum tuam, et \textbf{déx}teram \textbf{tu}am,~* de médio sinu tu\textit{o} \textit{in} \textbf{fi}nem?
 & \textit{\small Why dost thou turn away thy hand: and thy right hand out of the midst of thy bosom for ever?
}\\
13.\enspace Deus autem Rex noster \textbf{an}te \textbf{s\'{\ae}}cula:~* operátus est salútem in mé\textit{di}\textit{o} \textbf{ter}ræ.
 & \textit{\small But God is our king before ages: he hath wrought salvation in the midst of the earth.
}\\
14.\enspace Tu confirmásti in virtúte \textbf{tu}a \textbf{ma}re:~* contribulásti cápita dracó\textit{num} \textit{in} \textbf{a}quis.
 & \textit{\small Thou by thy strength didst make the sea firm: thou didst crush the heads of the dragons in the waters.
}\\
15.\enspace Tu confregísti cápi\textbf{ta} dra\textbf{có}nis:~* dedísti eum escam pópu\textit{lis} \textit{Æ}\textbf{thí}opum.
 & \textit{\small Thou hast broken the heads of the dragon: thou hast given him to be meat for the people of the Ethiopians.
}\\
16.\enspace Tu dirupísti fontes, \textbf{et} tor\textbf{rén}tes~* tu siccásti flú\textit{vi}\textit{os} \textbf{E}than.
 & \textit{\small Thou hast broken up the fountains and the torrents: thou hast dried up the Ethan rivers.
}\\
17.\enspace Tuus est dies, et \textbf{tu}a \textbf{est} nox:~* tu fabricátus es auró\textit{ram} \textit{et} \textbf{so}lem.
 & \textit{\small Thine is the day, and thine is the night: thou hast made the morning light and the sun.
}\\
18.\enspace Tu fecísti omnes \textbf{tér}minos \textbf{ter}ræ:~* æstátem et ver tu plas\textit{más}\textit{ti} \textbf{e}a.
 & \textit{\small Thou hast made all the borders of the earth: the summer and the spring were formed by thee.
}\\
19.\enspace Memor esto hujus, inimícus imprope\textbf{rá}vit \textbf{Dó}mino:~* et pópulus insípiens incitávit \textit{no}\textit{men} \textbf{tu}um.
 & \textit{\small Remember this, the enemy hath reproached the Lord: and a foolish people hath provoked thy name.
}\\
20.\enspace Ne tradas béstiis ánimas confi\textbf{tén}tes \textbf{ti}bi,~* et ánimas páuperum tuórum ne obliviscá\textit{ris} \textit{in} \textbf{fi}nem.
 & \textit{\small Deliver not up to beasts the souls that confess to thee: and forget not to the end the souls of thy poor.
}\\
21.\enspace Réspice in testa\textbf{mén}tum \textbf{tu}um:~* quia repléti sunt, qui obscuráti sunt terræ dómibus in\textit{i}\textit{qui}\textbf{tá}tum.
 & \textit{\small Have regard to thy covenant: for they that are the obscure of the earth have been filled with dwellings of iniquity.
}\\
22.\enspace Ne avertátur húmilis \textbf{fac}tus con\textbf{fú}sus:~* pauper et inops laudábunt \textit{no}\textit{men} \textbf{tu}um.
 & \textit{\small Let not the humble be turned away with confusion: the poor and needy shall praise thy name.
}\\
23.\enspace Exsúrge, Deus, júdica \textbf{cau}sam \textbf{tu}am:~* memor esto improperiórum tuórum, eórum quæ ab insipiénte sunt \textit{to}\textit{ta} \textbf{di}e.
 & \textit{\small Arise, O God, judge thy own cause: remember thy reproaches with which the foolish man hath reproached thee all the day.
}\\
24.\enspace Ne obliviscáris voces inimi\textbf{có}rum tu\textbf{ó}rum:~* supérbia eórum, qui te odérunt, a\textit{scén}\textit{dit} \textbf{sem}per. & \textit{\small Forget not the voices of thy enemies: the pride of them that hate thee ascendeth continually.}\\
\end{longtable}