\begin{longtable}{@{\hskip0pt} p{10cm} | p{6cm} @{\hskip0pt}}
2.\enspace Narrábimus mira\textbf{bí}lia \textbf{tu}a:~* cum accépero tempus, ego justítias \textbf{ju}di\textbf{cá}bo.
 & \textit{\small We will relate thy wondrous works: when I shall take a time, I will judge justices.
}\\
3.\enspace Liquefácta est terra, et omnes qui hábi\textbf{tant} in \textbf{e}a:~* ego confirmávi co\textbf{lúm}nas \textbf{e}jus.
 & \textit{\small The earth is melted, and all that dwell therein: I have established the pillars thereof.
}\\
4.\enspace Dixi iníquis: Nolíte in\textbf{í}que \textbf{á}gere:~* et delinquéntibus: Nolíte exal\textbf{tá}re \textbf{cor}nu:
 & \textit{\small I said to the wicked: Do not act wickedly: and to the sinners: Lift not up the horn.
}\\
5.\enspace Nolíte extóllere in altum \textbf{cor}nu \textbf{ves}trum:~* nolíte loqui advérsus Deum in\textbf{i}qui\textbf{tá}tem.
 & \textit{\small Lift not up your horn on high: speak not iniquity against God.
}\\
6.\enspace Quia neque ab Oriénte, neque ab Occidénte, neque a de\textbf{sér}tis \textbf{món}tibus:~* quóniam \textbf{De}us \textbf{ju}dex est.
 & \textit{\small For neither from the east, nor from the west, nor from the desert hills: for God is the judge.
}\\
7.\enspace Hunc humíliat, et \textbf{hunc} ex\textbf{ál}tat:~* quia calix in manu Dómini vini meri \textbf{ple}nus \textbf{mis}to.
 & \textit{\small One he putteth down, and another he lifteth up: for in the hand of the Lord there is a cup of strong wine full of mixture.
}\\
8.\enspace Et inclinávit ex hoc in hoc:~\GreDagger\ verúmtamen fæx ejus non est ex\textbf{i}na\textbf{ní}ta:~* bibent omnes pecca\textbf{tó}res \textbf{ter}ræ.
 & \textit{\small And he hath poured it out from this to that: but the dregs thereof are not emptied: all the sinners of the earth shall drink.
}\\
9.\enspace Ego autem annunti\textbf{á}bo in \textbf{s\'{\ae}}culum:~* cantábo \textbf{De}o \textbf{Ja}cob.
 & \textit{\small But I will declare for ever: I will sing to the God of Jacob.
}\\
10.\enspace Et ómnia córnua pecca\textbf{tó}rum con\textbf{frín}gam:~* et exaltabúntur \textbf{cór}nua \textbf{jus}ti. & \textit{\small And I will break all the horns of sinners: but the horns of the just shall be exalted.}\\
\end{longtable}