\begin{longtable}{@{\hskip0pt} p{10cm} | p{6cm} @{\hskip0pt}}
2.\enspace Et factus est in pace locus \textbf{e}jus:~* et habitátio e\textit{jus} \textit{in} \textbf{Si}on.
 & \textit{\small And his place is in peace: and his abode in Sion:
}\\
3.\enspace Ibi confrégit poténtias \textbf{ár}cuum:~* scutum, gládi\textit{um}, \textit{et} \textbf{bel}lum.
 & \textit{\small There hath he broken the powers of bows, the shield, the sword, and the battle.
}\\
4.\enspace Illúminans tu mirabíliter a móntibus æ\textbf{tér}nis:~* turbáti sunt omnes insipi\textit{én}\textit{tes} \textbf{cor}de.
 & \textit{\small Thou enlightenest wonderfully from the everlasting hills. All the foolish of heart were troubled.
}\\
5.\enspace Dormiérunt somnum \textbf{su}um:~* et nihil invenérunt omnes viri divitiárum in má\textit{ni}\textit{bus} \textbf{su}is.
 & \textit{\small They have slept their sleep; and all the men of riches have found nothing in their hands.
}\\
6.\enspace Ab increpatióne tua, Deus \textbf{Ja}cob,~* dormitavérunt qui ascen\textit{dé}\textit{runt} \textbf{e}quos.
 & \textit{\small At thy rebuke, O God of Jacob, they have all slumbered that mounted on horseback.
}\\
7.\enspace Tu terríbilis es, et quis resístet \textbf{ti}bi?~* ex tunc \textit{i}\textit{ra} \textbf{tu}a.
 & \textit{\small Thou art terrible, and who shall resist thee? from that time thy wrath.
}\\
8.\enspace De cælo audítum fecísti ju\textbf{dí}cium:~* terra trémuit \textit{et} \textit{qui}\textbf{é}vit.
 & \textit{\small Thou hast caused judgment to be heard from heaven: the earth trembled and was still,
}\\
9.\enspace Cum exsúrgeret in judícium \textbf{De}us,~* ut salvos fáceret omnes mansu\textit{é}\textit{tos} \textbf{ter}ræ.
 & \textit{\small When God arose in judgment, to save all the meek of the earth.
}\\
10.\enspace Quóniam cogitátio hóminis confitébitur \textbf{ti}bi:~* et relíquiæ cogitatiónis diem festum \textit{a}\textit{gent} \textbf{ti}bi.
 & \textit{\small For the thought of man shall give praise to thee: and the remainders of the thought shall keep holiday to thee.
}\\
11.\enspace Vovéte, et réddite Dómino Deo \textbf{ves}tro:~* omnes, qui in circúitu ejus af\textit{fér}\textit{tis} \textbf{mú}nera.
 & \textit{\small Vow ye, and pay to the Lord your God: all you that are round about him bring presents.
}\\
12.\enspace Terríbili et ei qui aufert spíritum \textbf{prín}cipum,~* terríbili apud \textit{re}\textit{ges} \textbf{ter}ræ. & \textit{\small To him that is terrible, even to him who taketh away the spirit of princes: to the terrible with the kings of the earth.}\\
\end{longtable}