\begin{longtable}{@{\hskip0pt} p{10cm} | p{6cm} @{\hskip0pt}}
2.\enspace In die tribulatiónis meæ Deum exquisívi,~\GreDagger\ mánibus meis nocte \textbf{con}tra \textbf{e}um:~* et non \textbf{sum} de\textbf{cép}tus.
 & \textit{\small In the day of my trouble I sought God, with my hands lifted up to him in the night, and I was not deceived.
}\\
3.\enspace Rénuit consolári ánima mea:~\GreDagger\ memor fui Dei, et delectátus sum, et ex\textbf{er}ci\textbf{tá}tus sum:~* et defécit \textbf{spí}ritus \textbf{me}us.
 & \textit{\small My soul refused to be comforted: I remembered God, and was delighted, and was exercised, and my spirit swooned away.
}\\
4.\enspace Anticipavérunt vigílias \textbf{ó}culi \textbf{me}i:~* turbátus sum, et non \textbf{sum} lo\textbf{cú}tus.
 & \textit{\small My eyes prevented the watches: I was troubled, and I spoke not.
}\\
5.\enspace Cogitávi \textbf{di}es an\textbf{tí}quos:~* et annos ætérnos in \textbf{men}te \textbf{há}bui.
 & \textit{\small I thought upon the days of old: and I had in my mind the eternal years.
}\\
6.\enspace Et meditátus sum nocte cum \textbf{cor}de \textbf{me}o,~* et exercitábar, et scopébam \textbf{spí}ritum \textbf{me}um.
 & \textit{\small And I meditated in the night with my own heart: and I was exercised and I swept my spirit.
}\\
7.\enspace Numquid in ætérnum pro\textbf{jí}ciet \textbf{De}us:~* aut non appónet ut complacíti\textbf{or} sit \textbf{ad}huc?
 & \textit{\small Will God then cast off for ever? or will he never be more favourable again?
}\\
8.\enspace Aut in finem misericórdiam \textbf{su}am ab\textbf{scín}det,~* a generatióne in gene\textbf{ra}ti\textbf{ó}nem?
 & \textit{\small Or will he cut off his mercy for ever, from generation to generation?
}\\
9.\enspace Aut obliviscétur mise\textbf{ré}ri \textbf{De}us:~* aut continébit in ira sua miseri\textbf{cór}dias \textbf{su}as?
 & \textit{\small Or will God forget to shew mercy? or will he in his anger shut up his mercies?
}\\
10.\enspace Et \textbf{di}xi: Nunc \textbf{c\oe}pi:~* hæc mutátio déxte\textbf{ræ} Ex\textbf{cél}si.
 & \textit{\small And I said, Now have I begun: this is the change of the right hand of the most High.
}\\
11.\enspace Memor fui \textbf{ó}perum \textbf{Dó}mini:~* quia memor ero ab inítio mirabíli\textbf{um} tu\textbf{ó}rum.
 & \textit{\small I remembered the works of the Lord: for I will be mindful of thy wonders from the beginning.
}\\
12.\enspace Et meditábor in ómnibus o\textbf{pé}ribus \textbf{tu}is:~* et in adinventiónibus tuis \textbf{ex}er\textbf{cé}bor.
 & \textit{\small And I will meditate on all thy works: and will be employed in thy inventions.
}\\
13.\enspace Deus, in sancto via tua:~\GreDagger\ quis Deus magnus sicut \textbf{De}us \textbf{nos}ter?~* tu es Deus qui facis \textbf{mi}ra\textbf{bí}lia.
 & \textit{\small Thy way, O God, is in the holy place: who is the great God like our God? Thou art the God that dost wonders.
}\\
14.\enspace Notam fecísti in pópulis vir\textbf{tú}tem \textbf{tu}am:~* redemísti in bráchio tuo pópulum tuum fílios \textbf{Ja}cob et \textbf{Jo}seph.
 & \textit{\small Thou hast made thy power known among the nations: with thy arm thou hast redeemed thy people the children of Jacob and of Joseph.
}\\
15.\enspace Vidérunt te aquæ, Deus, vi\textbf{dé}runt te \textbf{a}quæ:~* et timuérunt et turbátæ \textbf{sunt} a\textbf{býs}si.
 & \textit{\small The waters saw thee, O God, the waters saw thee: and they were afraid, and the depths were troubled.
}\\
16.\enspace Multitúdo sóni\textbf{tus} a\textbf{quá}rum:~* vocem de\textbf{dé}runt \textbf{nu}bes.
 & \textit{\small Great was the noise of the waters: the clouds sent out a sound.
}\\
17.\enspace Etenim sagíttæ \textbf{tu}æ \textbf{tráns}eunt:~* vox tonítrui \textbf{tu}i in \textbf{ro}ta.
 & \textit{\small For thy arrows pass: the voice of thy thunder in a wheel.
}\\
18.\enspace Illuxérunt coruscatiónes tuæ \textbf{or}bi \textbf{ter}ræ:~* commóta est, et con\textbf{tré}muit \textbf{ter}ra.
 & \textit{\small Thy lightnings enlightened the world: the earth shook and trembled.
}\\
19.\enspace In mari via tua, et sémitæ tuæ in \textbf{a}quis \textbf{mul}tis:~* et vestígia tua non \textbf{co}gno\textbf{scén}tur.
 & \textit{\small Thy way is in the sea, and thy paths in many waters: and thy footsteps shall not be known.
}\\
20.\enspace Deduxísti sicut oves \textbf{pó}pulum \textbf{tu}um,~* in manu Móy\textbf{si} et \textbf{A}aron. & \textit{\small Thou hast conducted thy people like sheep, by the hand of Moses and Aaron.}\\
\end{longtable}