% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

\documentclass[11pt, twoside]{report}

\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[bitstream-charter]{mathdesign}
\usepackage{bbding}
\usepackage{ragged2e}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}

\usepackage[autocompile]{gregoriotex}

\titleformat{\chapter}[block]{\huge\scshape\filcenter}{}{1ex}{}
\titleformat{\section}[block]{\LARGE\scshape\filcenter}{}{1ex}{}
\titleformat{\subsection}[block]{\Large\scshape\filcenter}{}{1ex}{}
\titleformat{\subsubsection}[block]{\large\bfseries\filcenter}{}{1ex}{}

\newenvironment{versicles}{\par\leavevmode\parskip=0pt\nopagebreak}{}

\begin{document}

\chapter*{{\Large Feria Quinta\\} In C\oe na Domini.}
\section*{Ad Matutinum.}

\begin{center}
Pater. Ave. Credo.
\end{center}

\subsection*{In primo Nocturno.}

\subsubsection*{Psalmus 68.}
\gresetinitiallines{1}
\gregorioscore{antiphonae/ferv-m1}
\gresetinitiallines{0}
\gregorioscore{psalmi/incipit/68-8c}
\input{psalmi/latini-anglicique/68-8.tex}

\subsubsection*{Psalmus 69.}
\gresetinitiallines{1}
\gregorioscore{antiphonae/ferv-m2}
\gresetinitiallines{0}
\gregorioscore{psalmi/incipit/69-8c}
\input{psalmi/latini-anglicique/69-8.tex}

\subsubsection*{Psalmus 70.}
\gresetinitiallines{1}
\gregorioscore{antiphonae/ferv-m3}
\gresetinitiallines{0}
\gregorioscore{psalmi/incipit/70-8c}
\input{psalmi/latini-anglicique/70-8.tex}

\gresetinitiallines{0}
\gregorioscore{versiculi/ferv-1}
Pater noster \textit{secreto.}

\subsubsection*{Lectio I.}
\input{lectiones/ferv-1.tex}
% \newpage
\gresetinitiallines{1}
\gregorioscore{responsaria/ferv-1}

\subsubsection*{Lectio II.}
\input{lectiones/ferv-2.tex}
% \newpage
\gresetinitiallines{1}
\gregorioscore{responsaria/ferv-2}

\subsubsection*{Lectio III.}
\input{lectiones/ferv-3.tex}
% \newpage
\gresetinitiallines{1}
\gregorioscore{responsaria/ferv-3}

\subsection*{In secundo Nocturno.}

\subsubsection*{Psalmus 71.}
\gresetinitiallines{1}
\gregorioscore{antiphonae/ferv-m4}
\gresetinitiallines{0}
\gregorioscore{psalmi/incipit/71-7c}
\input{psalmi/latini-anglicique/71-7.tex}

\subsubsection*{Psalmus 72.}
\gresetinitiallines{1}
\gregorioscore{antiphonae/ferv-m5}
\gresetinitiallines{0}
\gregorioscore{psalmi/incipit/72-8c}
\input{psalmi/latini-anglicique/72-8.tex}

\subsubsection*{Psalmus 73.}
\gresetinitiallines{1}
\gregorioscore{antiphonae/ferv-m6}
\gresetinitiallines{0}
\gregorioscore{psalmi/incipit/73-1g}
\input{psalmi/latini-anglicique/70-8.tex}

\gresetinitiallines{0}
\gregorioscore{versiculi/ferv-2}
Pater noster \textit{secreto.}

\subsubsection*{Lectio IV.}
\input{lectiones/ferv-4.tex}
% \newpage
\gresetinitiallines{1}
\gregorioscore{responsaria/ferv-4}

\subsubsection*{Lectio V.}
\input{lectiones/ferv-5.tex}
% \newpage
\gresetinitiallines{1}
\gregorioscore{responsaria/ferv-5}

\subsubsection*{Lectio VI.}
\input{lectiones/ferv-6.tex}
% \newpage
\gresetinitiallines{1}
\gregorioscore{responsaria/ferv-6}

\subsection*{In tertio Nocturno.}

\subsubsection*{Psalmus 74.}
\gresetinitiallines{1}
\gregorioscore{antiphonae/ferv-m7}
\gresetinitiallines{0}
\gregorioscore{psalmi/incipit/74-7c}
\input{psalmi/latini-anglicique/74-7.tex}

\subsubsection*{Psalmus 75.}
\gresetinitiallines{1}
\gregorioscore{antiphonae/ferv-m8}
\gresetinitiallines{0}
\gregorioscore{psalmi/incipit/75-8c}
\input{psalmi/latini-anglicique/75-8.tex}

\subsubsection*{Psalmus 76.}
\gresetinitiallines{1}
\gregorioscore{antiphonae/ferv-m9}
\gresetinitiallines{0}
\gregorioscore{psalmi/incipit/76-7a}
\input{psalmi/latini-anglicique/76-7.tex}

\gresetinitiallines{0}
\gregorioscore{versiculi/ferv-3}
Pater noster \textit{secreto.}

\subsubsection*{Lectio VII.}
\input{lectiones/ferv-7.tex}
% \newpage
\gresetinitiallines{1}
\gregorioscore{responsaria/ferv-7}

\subsubsection*{Lectio VIII.}
\input{lectiones/ferv-8.tex}
% \newpage
\gresetinitiallines{1}
\gregorioscore{responsaria/ferv-8}

\subsubsection*{Lectio IX.}
\input{lectiones/ferv-9.tex}
% \newpage
\gresetinitiallines{1}
\gregorioscore{responsaria/ferv-9}

\section*{Ad Laudes.}

\subsubsection*{Psalmus 50.}
\gresetinitiallines{1}
\gregorioscore{antiphonae/ferv-l1}
\gresetinitiallines{0}
\gregorioscore{psalmi/incipit/50-8G}
\input{psalmi/latini-anglicique/50-8.tex}

\end{document}